### 2019-02-23 soc.tex
update paragraph and title formatting
It seems that em wasn't working the way I thought it was. The document should now be in line with the formatting requirements.
adjust image border thickness
1pt was just a little too thick
update Klíčová slova formatting
I have no idea why this was formatted this way...

\setlength{\fboxsep}{0pt}                       % image border separation
\setlength{\fboxrule}{1pt}                      % image border thickness

@@

\setlength\parindent{0pt}                       % paragraph indentation
\setlength{\parskip}{1.2em}                     % paragraph spacing

@@

% TITLE FORMATTING %
%-================-%
\usepackage{titlesec}

% title formatting
\titleformat{\section}{\bfseries\scshape\fontsize{18}{21.6}\selectfont}{\thesection}{1em}{}
\titleformat{\subsection}{\bfseries\fontsize{16}{19.2}\selectfont}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\bfseries\fontsize{14}{16.8}\selectfont}{\thesubsubsection}{1em}{}

% title spacing
\titlespacing{\section}{0pt}{0pt}{0.3em}
\titlespacing{\subsection}{0pt}{0pt}{0.2em}
\titlespacing{\subsubsection}{0pt}{0pt}{0.0em}

@@

  \subsection*{\fontsize{18}{21.6}\selectfont\normalfont\textbf{Klíčová slova}}
  robotika; webová stránka; vzdělávání

>>>>

\setlength{\fboxsep}{0pt}                       % image border separation
\setlength{\fboxrule}{0.5pt}                    % image border thickness

@@

@@

% TEXT FORMATTING %
%-================-%
\usepackage{titlesec}

% titles have sizes 18pt, 16pt and 14pt, respectively
% the space between the number and the text of the title is 1em = 10pt
\titleformat{\section}{\bfseries\scshape\fontsize{18pt}{21.6}\selectfont}{\thesection}{1em}{}
\titleformat{\subsection}{\bfseries\fontsize{16pt}{19.2}\selectfont}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\bfseries\fontsize{14pt}{16.8}\selectfont}{\thesubsubsection}{1em}{}

\titlespacing{\section}      {0pt}{0pt}{6pt}    % 18pt (12pt + 6pt)
\titlespacing{\subsection}   {0pt}{0pt}{4pt}    % 16pt (12pt + 4pt)
\titlespacing{\subsubsection}{0pt}{0pt}{2pt}    % 14pt (12pt + 2pt)

\renewcommand{\baselinestretch}{1.15}           % baseline stretch

\setlength\parindent{0pt}                       % 0pt paragraph indentation
\setlength\parskip{12pt}                        % 12pt paragraph spacing

@@

  \section*{\normalfont\textbf{Klíčová slova}}
  robotika; webová stránka; vzdělávání
